```{r}
library(fitdistrplus)
library(survminer)
library(tidyverse)
library(ggplot2)
library(survival)
library(skimr)
```
```{r}
TEST = TRUE
ROOT = 'C://Users//corma//Documents//GitHub//18650-Accelerated-Battery-Life-Testing//'
```
```{r}
if (TEST) {
  data_path = '/battery_alt_dataset/regular_alt_batteries/battery00.csv'
  print('Running in test mode')
} else {
  data_path = '/battery_alt_dataset/regular_alt_batteries.csv'
  print('Running in production mode')
}
```
```{r}
data = read_csv(paste0(ROOT, data_path))
```
```{r}
head(data)
```

```{r}
skim(data)
```
```{r}
colnames(data)
```
["start_time", "time", "mode", "voltage_charger", "temperature_battery", "voltage_load", "current_load", "temperature_mosfet"   "temperature_resistor", "mission_type"]
```{r}
# create a km plot from time
fit = survfit(Surv(time, mode) ~ 1, data = data)
ggsurvplot(fit, data = data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Single Family Homes")
```
- mode: -1 = discharge, 0 = rest, 1 = charge
- Discharge means that the battery is discharging
- Charge means the battery is taking in charge
- Rest means the battery is neither charging nor discharging
```{r}
discharge_data = data %>% filter(mode == -1)
rest_data = data %>% filter(mode == 0)
charge_data = data %>% filter(mode == 1)
```
```{r}
# discharge_fit = survfit(Surv(time, mode) ~ 1, data = discharge_data)
rest_fit = survfit(Surv(time, mode) ~ 1, data = rest_data)
charge_fit = survfit(Surv(time, mode) ~ 1, data = charge_data)
```
```{r}
# ggsurvplot(discharge_fit, data = discharge_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Discharging Batteries")
```
```{r}
ggsurvplot(rest_fit, data = rest_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Batteries at Rest")
```
```{r}
ggsurvplot(charge_fit, data = charge_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Charging Batteries")
```
Acelerating factors are Voltage and Temperature
- voltage charger: [V] (continuous battery pack voltage measurement right after the connection of the battery pack to the charger board)
- temperature battery: [C] (continuous temperature measurement on the battery cell electrode surface)
```{r}
alt_data = charge_data %>% mutate(
  alt = voltage_charger * temperature_battery
)
skim(alt_data[,'alt'])
```
```{r}
# plot the distribution of alt
ggplot(alt_data, aes(x = alt)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of ALT") +
  theme_minimal()
```
```{r}
ggplot(alt_data, aes(x = temperature_battery)) +
        geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
        ggtitle("Distribution of Temperature") +
        theme_minimal()
```
```{r}
# plot the distibution of Voltage and Temperature
ggplot(alt_data, aes(x = voltage_charger)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of Voltage") +
  theme_minimal()
```
```{r}
# set the acelearting factor AF
alt_data = alt_data %>% mutate(
  AF = as.integer(alt / 10)
)
```
```{r}
# plot the distribution of AF
ggplot(alt_data, aes(x = AF)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of AF") +
  theme_minimal()

```
```{r}
#show <20, 20-40, and 40-60
AF_group = alt_data %>% mutate(
            AF1 = ifelse(AF < 20, 1, 0),
            AF2 = ifelse(AF >= 20 & AF < 40, 1, 0),
            AF3 = ifelse(AF >= 40 & AF < 60, 1, 0)
    )
AF1_fit = survfit(Surv(time, mode) ~ AF1, data = AF_group)
AF2_fit = survfit(Surv(time, mode) ~ AF2, data = AF_group)
AF3_fit = survfit(Surv(time, mode) ~ AF3, data = AF_group)
```
```{r}
ggsurvplot(AF1_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for AF < 20")
ggsurvplot(AF2_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for 20 <= AF < 40")
ggsurvplot(AF3_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for 40 <= AF < 60")
```
```{r}

```
