```{r}
library(fitdistrplus)
library(survminer)
library(tidyverse)
library(ggplot2)
library(survival)
library(skimr)
library(grid)
library(gridExtra)
```
```{r}
ROOT = 'C://Users//corma//Documents//GitHub//18650-Accelerated-Battery-Life-Testing//'
# read in regular.csv
data = read_csv('second.csv')
```
```{r}
colnames(data)
```
[1] "...1"                "dischargePhase"      "voltage_charger"
[4] "temperature_battery" "current_load"        "time_end"

```{r}
# since every row is a failure event, we can just use the time_end column
fit = survfit(Surv(time_end) ~ 1, data = data)
ggsurvplot(fit, data = data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Batteries")
```
```{r}
# histogram of time_end
ggplot(data, aes(x = time_end)) +
  geom_histogram(bins = 30) +
  ggtitle("Histogram of Time to Failure")
```


```{r}
# filter out temps < 0
data = data %>% filter(temperature_battery > 0)
# drop times at 0
data = data %>% filter(time_end > 10)
# turn temperature into the Arrhenius model and voltage into log voltage

data = data %>%
  mutate(arr_temp = 11605/(temperature_battery + 273.15),
         log_volt = log10(voltage_charger))

# graph time x temperature_battery

# color by magma
ggplot(data, aes(x =temperature_battery, y = time_end, color= current_load)) +
  geom_point() + # color magma
  scale_color_viridis_c() +
  ggtitle("Time to Failure vs Temperature Battery")
```

```{r}
# add a col for failure (they all failed)
data$failure = 1
# drop instances where time_end is NA or 0
data = data %>% filter(!is.na(time_end) & time_end != 0)
```
```{r}
# create a weibull model for the time to failure using Current Load, Voltage Charger, and Temperature Battery
weibull_fit = survreg(Surv(time_end, failure) ~ current_load +
  log_volt +
  arr_temp
                      , data = data, dist = "weibull")
summary(weibull_fit)
```
(Intercept)                         18.07880    0.46667  38.7 <2e-16
current_load                        -0.04667    0.00359 -13.0 <2e-16
voltage_charger                     -1.89913    0.06973 -27.2 <2e-16
temperature_battery                 -0.35592    0.01466 -24.3 <2e-16
voltage_charger:temperature_battery  0.06021    0.00228  26.4 <2e-16
Log(scale)                          -0.76061    0.00000  -Inf <2e-16

Scale= 0.467

Weibull distribution
Loglik(model)= -40858.6   Loglik(intercept only)= -36321
Chisq= -9075.19 on 4 degrees of freedom, p= 1
Number of Newton-Raphson Iterations: 30
n= 4863


# this is tess us that the current load, voltage charger, temperature battery, and the interaction between voltage charger and temperature battery are all significant predictors of time to failure

```{r}
# a function that takes a model and returns the mse, aic, and r^2
model_metrics = function(model, data) {
  pred = predict(model, type = "response")
  mse = mean((pred - data$time_end)^2)
  aic = AIC(model)
  r2 = 1 - mse / var(data$time_end)
  print("MSE:")
  print(mse)
  print("AIC:")
  print(aic)
  print("R^2:")
  print(r2)
  return(c(mse, aic, r2))
}
model_metrics(weibull_fit, data)
```
```{r}
# graph the predicted vs actual time to failure
pred = predict(weibull_fit, type = "response")
secondplot = ggplot(data, aes(x = time_end, y = pred)) +
  geom_point(color='palegreen4',alpha=.5) +
  geom_abline(intercept = 0, slope = 1, color = "red") +
  ylab("Predicted Time to Failure") + 
  theme(axis.title.y = element_text(size=14), plot.subtitle = element_text(size = 18),axis.text = element_text(size=12)) +
  xlab('Actual Time to Failure')+
  labs(subtitle='Second Life Batteries') +
  xlim(0,3500)
```

```{r}
reg = read_csv('regular.csv')

# filter out temps < 0
reg = reg %>% filter(temperature_battery > 0)
# drop times at 0
reg = reg %>% filter(time_end > 10)
# graph time x temperature_battery

reg$failure = 1
# drop instances where time_end is NA or 0
reg = reg %>% filter(!is.na(time_end) & time_end != 0)

# create a weibull model for the time to failure using Current Load, Voltage Charger, and Temperature Battery
weibull_fitreg = survreg(Surv(time_end, failure) ~ current_load +
  voltage_charger +
  temperature_battery
                      , data = reg, dist = "weibull")
summary(weibull_fitreg)
```
```{r}
predreg = predict(weibull_fitreg, type = "response")
regplot = ggplot(reg, aes(x = time_end, y = predreg)) +
  geom_point(color='cyan4',alpha=.5) +
  geom_abline(intercept = 0, slope = 1, color = "red") +
  ylab("Predicted Time to Failure") + 
  xlab(' ') +
  theme(axis.title.y = element_text(size=14),plot.subtitle = element_text(size = 18),plot.title = element_text(size = 24),axis.text = element_text(size=12)) +
  labs(subtitle='Regular Batteries')+
  ggtitle('Predicted Time to Failure vs Actual') +
  xlim(0,3500)
```

```{r}
recom = read_csv('recommissioned.csv')

# filter out temps < 0
recom = recom %>% filter(temperature_battery > 0)
# drop times at 0
recom = recom %>% filter(time_end > 10)
# graph time x temperature_battery

recom$failure = 1
# drop instances where time_end is NA or 0
recom = recom %>% filter(!is.na(time_end) & time_end != 0)

# create a weibull model for the time to failure using Current Load, Voltage Charger, and Temperature Battery
weibull_fitrecom = survreg(Surv(time_end, failure) ~ current_load +
  voltage_charger +
  temperature_battery
                      , data = recom, dist = "weibull")
summary(weibull_fitrecom)
```
```{r}

predrecom = predict(weibull_fitrecom, type = "response")
recomplot = ggplot(recom, aes(x = time_end, y = predrecom)) +
  geom_point(color='khaki4',alpha=.5) +
  geom_abline(intercept = 0, slope = 1, color = "red") +
  ylab("Predicted Time to Failure") +
  theme(axis.title.y = element_text(size=14), plot.subtitle = element_text(size = 18),axis.text = element_text(size=12)) +
  xlab(' ')+
  labs(subtitle='Recommissioned Batteries')+
  xlim(0,3500)
```

```{r}
weibullreg = grid.arrange(regplot,recomplot,secondplot,ncol=1)
ggsave('weibullregression.png',weibullreg, width=10,height=16)
```

