```{r}
library(fitdistrplus)
library(survminer)
library(tidyverse)
library(ggplot2)
library(survival)
library(skimr)
library(gridExtra)
library(grid)
```

```{r}
regular = read_csv('regular.csv')
recom = read_csv('recommissioned.csv')
second = read_csv('second.csv')
```
```{r}
head(regular)
```

```{r}
skim(regular)
```
```{r}
colnames(regular)
```
["start_time", "time", "mode", "voltage_charger", "temperature_battery", "voltage_load", "current_load", "temperature_mosfet"   "temperature_resistor", "mission_type"]
```{r}
# create a km plot from time
regular = regular %>%
  mutate(type = 'regular') %>%
  filter(time_end > 10)

recom = recom %>%
  mutate(type = 'recommissioned') %>%
  filter(time_end > 10)

second = recom %>%
  mutate(type = 'second_life') %>%
  filter(time_end > 10)

batteries = rbind(regular,recom,second)
```

```{r}
get_time_at_50 <- function(surv_fit) {
  # Find the time where the survival drops to 50% or closest to it
  index <- which.min(abs(surv_fit$surv - 0.5))
  time_50 <- surv_fit$time[index]
  return(time_50)
}

recom_time_50 <- get_time_at_50(recom_fit)
regular_time_50 <- get_time_at_50(regular_fit)
```

```{r, echo=FALSE}
offset = 1000
textsize = 5

recom_fit = survfit(Surv(time_end, mode) ~ 1, data=recom)
recom_time_50 <- get_time_at_50(recom_fit)
recom_plot = ggsurvplot(recom_fit, data = recom, pval = TRUE, surv.median.line = "hv", conf.int = TRUE, palette='blue')
recom_plot = recom_plot$plot + ggtitle('Recommissioned') + theme(plot.title = element_text(size = 15, face = "bold"), axis.text = element_text(size=8),axis.title.y = element_blank(),axis.ticks.y = element_blank(),axis.text.y=element_blank(),axis.line.y=element_blank(),legend.title=element_blank(),legend.position="none")+ geom_hline(yintercept = 0.5, linetype = "dashed") + geom_point(aes(x = recom_time_50, y = 0.5),color='black',size=3)+
  geom_text(aes(x = recom_time_50+offset, y = 0.5,label=paste0("50% (", round(recom_time_50, 2), ")")),vjust = -1, size = textsize)

regular_fit = survfit(Surv(time_end, mode) ~ 1, data=regular)
regular_time_50 <- get_time_at_50(regular_fit)
regular_plot = ggsurvplot(regular_fit, data = regular, pval = TRUE, surv.median.line = "hv", conf.int = TRUE, palette = 'red')
regular_plot = regular_plot$plot + ggtitle('Regular') + theme(plot.title = element_text(size = 15, face = "bold"),legend.title=element_blank(),legend.position="none") + geom_hline(yintercept = 0.5, linetype = "dashed") + geom_point(aes(x = regular_time_50, y = 0.5),color='black',size=3)+
  geom_text(aes(x = regular_time_50+offset+150, y = 0.5,label=paste0("50% (", round(regular_time_50, 2), ")")),vjust = -1, size = textsize)

second_fit = survfit(Surv(time_end, mode) ~ 1, data=second)
second_time_50 <- get_time_at_50(second_fit)
second_plot = ggsurvplot(second_fit, data = second, pval = TRUE, surv.median.line = "hv", conf.int = TRUE, palette = 'forestgreen')
second_plot = second_plot$plot + ggtitle('Second Life') + theme(plot.title = element_text(size = 15, face = "bold"), legend.title=element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank(),axis.text.y=element_blank(), legend.position="none",axis.line.y = element_blank()) + geom_hline(yintercept = 0.5, linetype = "dashed") + geom_point(aes(x = second_time_50, y = 0.5),color='black',size=3)+
  geom_text(aes(x = second_time_50+offset, y = 0.5,label=paste0("50% (", round(second_time_50, 2), ")")),vjust = -1, size = textsize)
```

```{r, echo = FALSE, fig.width=10, fig.height=8}
grid.arrange(regular_plot,second_plot,recom_plot,ncol=3, top = textGrob('Kaplan-Meyer Curves for Battery Packs',gp=gpar(fontsize=20,face='bold')))
ggsave('kmcurves.png')
```

```{r}
fit = survfit(Surv(time_end, mode) ~ type, data = batteries)
ggsurvplot_facet(fit, data = batteries, facet.by = 'type', pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Batteries")
```
- mode: -1 = discharge, 0 = rest, 1 = charge
- Discharge means that the battery is discharging
- Charge means the battery is taking in charge
- Rest means the battery is neither charging nor discharging
```{r}
discharge_data = data %>% filter(mode == -1)
rest_data = data %>% filter(mode == 0)
charge_data = data %>% filter(mode == 1)
```
```{r}
# discharge_fit = survfit(Surv(time, mode) ~ 1, data = discharge_data)
rest_fit = survfit(Surv(time, mode) ~ 1, data = rest_data)
charge_fit = survfit(Surv(time, mode) ~ 1, data = charge_data)
```
```{r}
# ggsurvplot(discharge_fit, data = discharge_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Discharging Batteries")
```
```{r}
ggsurvplot(rest_fit, data = rest_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Batteries at Rest")
```
```{r}
ggsurvplot(charge_fit, data = charge_data, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for Charging Batteries")
```
Acelerating factors are Voltage and Temperature
- voltage charger: [V] (continuous battery pack voltage measurement right after the connection of the battery pack to the charger board)
- temperature battery: [C] (continuous temperature measurement on the battery cell electrode surface)
```{r}
alt_data = charge_data %>% mutate(
  alt = voltage_charger * temperature_battery
)
skim(alt_data[,'alt'])
```
```{r}
# plot the distribution of alt
ggplot(alt_data, aes(x = alt)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of ALT") +
  theme_minimal()
```
```{r}
ggplot(alt_data, aes(x = temperature_battery)) +
        geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
        ggtitle("Distribution of Temperature") +
        theme_minimal()
```
```{r}
# plot the distibution of Voltage and Temperature
ggplot(alt_data, aes(x = voltage_charger)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of Voltage") +
  theme_minimal()
```
```{r}
# plot time to failure
ggplot(alt_data, aes(x = time)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of Time to Failure") +
  theme_minimal()
```
```{r}
# set the acelearting factor AF
alt_data = alt_data %>% mutate(
  AF = as.integer(alt / 10)
)
```
```{r}
# plot the distribution of AF
ggplot(alt_data, aes(x = AF)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  ggtitle("Distribution of AF") +
  theme_minimal()

```
```{r}
#show <20, 20-40, and 40-60
AF_group = alt_data %>% mutate(
            AF1 = ifelse(AF < 20, 1, 0),
            AF2 = ifelse(AF >= 20 & AF < 40, 1, 0),
            AF3 = ifelse(AF >= 40 & AF < 60, 1, 0)
    )
AF1_fit = survfit(Surv(time, mode) ~ AF1, data = AF_group)
AF2_fit = survfit(Surv(time, mode) ~ AF2, data = AF_group)
AF3_fit = survfit(Surv(time, mode) ~ AF3, data = AF_group)
```
```{r}
ggsurvplot(AF1_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for AF < 20")
ggsurvplot(AF2_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for 20 <= AF < 40")
ggsurvplot(AF3_fit, data = AF_group, pval = TRUE, surv.median.line = "hv", conf.int = TRUE) + ggtitle("KM curve for 40 <= AF < 60")
```

ttf~weibull(m=b0+b1Temp + b2Volt + b3Temp*Volt + Type, theta = 1/lambda)
temp = 11605/(tempC + 273.15)
volt = log(volt)
```{r}
regular_batteries = read_csv(paste0(ROOT, '/battery_alt_dataset/regular_alt_batteries.csv'))
# filter for only charging batteries
regular_batteries = regular_batteries %>% filter(mode == 1)
# create _temp and _volt
regular_batteries = regular_batteries %>% mutate(
  temp = 11605/(temperature_battery + 273.15),
  volt = log(voltage_charger)
)
```
```{r}
model = survreg(Surv(time, mode) ~ temp + volt + temp*volt, data = regular_batteries, dist = "weibull", control = survreg.control(maxiter = 1000000))
summary(model)
```
```{r}
library(car)

# Check for multicollinearity
vif_data = regular_batteries %>% select(temp, volt, mission_type)
vif(vif_data)
```
